ESI for "Probabilistic determination of the effect of a deep eutectic solvent on the structure of lipid monolayers"

### 2018-07-09 reports/paper.tex
first full version

\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Probabilistic determination of the effect of a deep-eutectic solvent on the structure of lipid monolayers}} \\%Article title goes here instead of the text "This is the title"
\vspace{0.3cm} & \vspace{0.3cm} \\

@@

The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the values found for the head group component volume is accurate for the given system. This further indicates that the literature values for the head group component volume found in the literature when solvated with water is not sufficient for modelling this system at the air-DES interface.

>>>>

\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{Bayesian determination of the effect of a deep-eutectic solvent on the structure of lipid monolayers}} \\%Article title goes here instead of the text "This is the title"
\vspace{0.3cm} & \vspace{0.3cm} \\

@@

The ability to fit the NR data, as shown in Figure \ref{fig:neutron} indicates that the values found for the head group component volume is accurate for the given system. This further indicates that the literature values for the head group component volume found in the literature when solvated with water is not sufficient for modelling this system at the air-DES interface. Additionall, it is also clear that despite the best effort it was not possible to form condensed phase monolayer of the phospholipid without the force available to a Langmuir trough. This is evident from the relatively high volume fractions of air in the tail layer and the high chain tilt angles adopted by the tails.
